---
title: "Stat 123 Homework 1"
author: "Jonathan Wilson"
date: "January 5, 2019"
output: word_document
---

```{r}
setwd("C:\\Users\\jon\\Documents\\School\\R\\HW\\HW1")
```
Load the mtcars dataset that comes preinstalled in R using the data() function.
```{r}
data(mtcars)#Load data from mtcars
```

Find the mean of the miles per gallon variable.
```{r}
mpg <- mtcars$mpg
mean(mpg)
```

Compute the linear correlation between the "mpg" and "cyl" variables. Hint: if you don't know which function to use, try typing "correlation" in the search bar of the help tab in RStudio. 
```{r}
cyl <- mtcars$cyl
cor(mpg, cyl)#cor.test gives more info cor() gives just the cor. 
```

Compute the linear correlation between the "mpg" and "gear" variables.
```{r}
gears <- mtcars$gear
cor(mpg, gears)
```

Find the mean of the "mpg" variable for each value of the "gear" variable.
```{r}
#Gear 3
gear3.table <- mtcars[mtcars$gear==3,]
mean(gear3.table$mpg)

#Gear 4
gear4.table <- mtcars[mtcars$gear==4,]
mean(gear4.table$mpg)

#Gear 5
gear5.table <- mtcars[mtcars$gear==5,]
mean(gear5.table$mpg)
```

Find the median of the "mpg" variable for each value of the "gear" variable.
```{r}
median(gear3.table$mpg)
median(gear4.table$mpg)
median(gear5.table$mpg)
```

Find the make and model of the car with the highest miles per gallon.  What are its "cyl" and "gear" values?
```{r}
max.mpg <- max(mtcars$mpg)
car <- mtcars[mtcars$mpg==max.mpg,]
car.type <- row.names(car)#Extracts the row name
car.type
```

