---
title: "Stat 123 Homework 15"
author: "Jonathan Wilson"
date: "February 18, 2019"
output: word_document
---
```{r}

knitr::opts_knit$set(root.dir = "C:\\Users\\jon\\Documents\\School\\R\\HW\\HW15")
#Make sure you are calling the right lib in the RIGHT ORDER!

library(plyr); library(magrittr); library(dplyr); library(data.table)
```
Data on the daily concentration of fine particles pollutant (PM2.5) for all
monitor sites in Utah County is available in .csv files attached to the assignment, 
with each file having data from a year. These files have the name format
"ad_viz_plotval_data-XXXX.csv" (where XXXX is place holder for the year).  

Write a function named 'air' that
takes a 'year' argument and returns a data.frame containing that data for
that year, suppressing the automatic conversion to factors.
```{r}
air <- function(year){
  file <- sprintf("ad_viz_plotval_data-%s.csv", year)
  data <- read.table(file, sep=",", header=TRUE, stringsAsFactors=FALSE)
  return(data)
}

```

Using lapply, make a list containing a data.frame for each year.
```{r}
data.list <- lapply(2009:2016, air)
```

Combine all the data.frames in the list to one data.frame (without losing any data).
```{r}
data <- rbindlist(data.list)
```


Summarize this big data.frame to yield a data.frame containing only the
average "DAILY_AQI_VALUE" and the average "Daily.Mean.PM2.5.Concentration" for each
value of "Date".
```{r}
avg.data <- data %>% group_by(Date) %>% summarize(DAILY_AQI_VALUE = mean(DAILY_AQI_VALUE), Daily.Mean.PM2.5.Concentration = mean(Daily.Mean.PM2.5.Concentration))
```

Produce a scatter plot of the average "Daily.Mean.PM2.5.Concentration" (on
the y-axis) and average "DAILY_AQI_VALUE" (on the x-axis).
```{r}
attach(avg.data)
my.plot <- plot(DAILY_AQI_VALUE, Daily.Mean.PM2.5.Concentration, main="Scatterplot Example", 
   xlab="DAILY_AQI_VALUE ", ylab="Daily.Mean.PM2.5.Concentration ", pch=19)

```

Add vertical lines at 50, 100, and 150 on the x-axis.  Hint: See the help for
the "abline" function.
```{r}
plot(DAILY_AQI_VALUE, Daily.Mean.PM2.5.Concentration, main="Scatterplot Example", 
   xlab="DAILY_AQI_VALUE ", ylab="Daily.Mean.PM2.5.Concentration ", pch=19)
abline(v=c(50, 100, 150), col=c("green","blue","red"))
```
