---
title: "Stat 123 Homework 3"
author: "Jonathan Wilson"
date: "January 11, 2019"
output: word_document
---
```{r}
#Make working directory global
knitr::opts_knit$set(root.dir = "C:\\Users\\jon\\Documents\\School\\R\\HW\\HW3")
```
Make a list containing three elements named "y2011", "y2012", and "y2013"
containing three data.frames of weather information for years 2011, 2012, and
2013 in Provo. You will need to read in the data found in the instructions.

```{r}
y2011 <- read.table("Weather2011.csv", sep=",", header=TRUE,
                  stringsAsFactors=FALSE)
y2012 <- read.table("Weather2012.csv", sep=",", header=TRUE,
                  stringsAsFactors=FALSE)
y2013 <- read.table("Weather2013.csv", sep=",", header=TRUE,
                  stringsAsFactors=FALSE)

weather.provo <- list(y2011, y2012, y2013) 
```

Using the list you created, how many days in 2011 had a maximum temperature above 90 degrees?  Watch out, there may be missing values!
```{r}
Temp.Max2011 <- weather.provo[[1]]$Temp.MaxF > 90 #Will give TRUE or FALSE.
sum(Temp.Max2011, na.rm = TRUE)#TRUE is 1 so sum all 1s
#na.rm gets rid of NAs
```


Using the list you created, how many days in 2012 had a maximum temperature above 90 degrees?
```{r}
Temp.Max2012 <- weather.provo[[2]]$Temp.MaxF > 90 #Will give TRUE or FALSE.
sum(Temp.Max2012, na.rm = TRUE)#TRUE is 1 so sum all 1s
#na.rm gets rid of NAs
```


Using the list you created, how many days in 2013 had a maximum temperature above 90 degrees?
```{r}
Temp.Max2013 <- weather.provo[[3]]$Temp.MaxF > 90 #Will give TRUE or FALSE.
sum(Temp.Max2013, na.rm = TRUE)#TRUE is 1 so sum all 1s
#na.rm gets rid of NAs
```
