---
title: "Stat 123 Homework 9"
author: "Jonathan Wilson"
date: "January 31, 2019"
output: word_document
---

```{r}

knitr::opts_knit$set(root.dir = "C:\\Users\\jon\\Documents\\School\\R\\HW\\HW9")
```
Generate vectors x and y of length 100 from a discrete distribution with four
outcomes using the sample function (i.e., x <- sample(1:4, 100,
replace=TRUE)).  Use a "for loop" to create a logical vector determining: 1.
which of the entries in the two vectors are the same and 2. the total number
of entries that are the same. Your answer to the first will be a vector of
length 100 and the answer to the second will be a single value (i.e., a
vector of length 1).
```{r}
x <- sample(1:4, 100, replace=TRUE)
y <- sample(1:4, 100, replace=TRUE)

#Matches?
n <- 0
m1 <- vector()
for (i in 1:length(x)){
  if( x[i] == y[i]){
    m1[i] <- 1
  }
  else{
    m1[i] <- 0
  }
  n <- n + 1
}
m1
n

```

Using your 'x' and 'y' variables from above, now do the same calculation
without a "for loop".  Thought questions (for which you don't need to provide
an answer): Which method is better?
```{r}
match2 <- (x == y)
match2
length(match2)
```
