---
title: "Stat 123 Homework 2"
author: "Jonathan Wilson"
date: "January 6, 2019"
output: word_document
---

```{r}

knitr::opts_knit$set(root.dir = "C:\\Users\\jon\\Documents\\School\\R\\HW\\HW2")
```


Using the file given in the instructions, read the daily interest in lds.org for 2014-06-09 through 2014-09-06 into an data.frame.
```{r}
#setwd("C:\\Users\\jon\\Documents\\School\\R\\HW\\HW2")
lds <- read.table("reportclean.csv", sep=",", header=TRUE,
                  stringsAsFactors=FALSE)
#lds
#str(lds)
#lds <- read.csv("reportclean.csv", stringsAsFactors=FALSE)
```

Name the variables in the data.frame "date" and "interest".
```{r}
names(lds) <- c("date","interest")

```

Replace the "date" character vector in the data.frame into a vector of Date objects of the same name.
```{r}

lds$date <- as.Date(lds$date, format="%m/%d/%Y")#, format = "%m/%d/%Y"

```

Use the "weekdays" function to define a new variable in the data.frame called "weekday" from the "date" variable.
```{r}
lds$weekday <- weekdays(as.Date(lds$date)) 
```

Find the mean of the interest variable across all Mondays.  
```{r}
mondays <- lds[lds$weekday=="Monday",]
mean.monday <- mean(mondays$interest)
mean.monday
```

Find the mean of the interest variable for the weekends.
```{r}
weekends <- lds[lds$weekday %in% c("Sunday","Saturday"),]
mean.weekends <- mean(weekends$interest)
mean.weekends
```

Find the mean of the interest variable for all weekdays.
```{r}
#By weekdays I am assuming that you mean only Mon-Fri. I could easily run a mean for either. 
weekdays <- subset(lds, !(lds$weekday %in% c("Sunday","Saturday")))
mean.weekdays <- mean(weekdays$interest)
mean.weekdays

```

Comment on whether you believe there is a statistically significant
difference between the mean interest on weekdays and weekends?  You don't
have to do a formal test.  We're asking for just your intuition after seeing
the data. Since your response won't be executable code, do not include it in an r chunk, or if you do, prefix your comments with R's comment character, #.


What are the median, minimum, and maximum interest?
```{r}
#The mean is much higher on the weekends. I would say it is statistically significant since more people are on 
#during the weekends. That is my idea. 
median.interest <- median(lds$interest)
median.interest
min.interest <- min(lds$interest)
min.interest
max.interest <- max(lds$interest)
max.interest
```


What is the correlation between interests one day apart?
```{r}
lag <- lds[1:89,]
x <- rep(c("2014-05-09",0,"Sunday"), ncol(lag))
lag <- rbind(x, lag)#Create lag in rows by one day
lag$interest <- as.integer(lag$interest)
cor(lds$interest, lag$interest)
```

