---
title: "Stat 123 Homework 14"
author: "Jonathan Wilson"
date: "February 13, 2019"
output: word_document
---
```{r}

knitr::opts_knit$set(root.dir = "C:\\Users\\jon\\Documents\\School\\R\\HW\\HW14")
#Make sure you are calling the right lib in the RIGHT ORDER!

library(plyr); library(magrittr); library(dplyr)
```

Load the "movies.Rbin" file.  Calculate the mean rating
for each level of MPAA rating (G, PG, etc.) using this data.  Hints:  You can
download the data in R using the 'load' function and you can access
the 'movies' data.frame by loading the R binary file with the 'load'
function.

```{r}
load("movies.Rbin")
movies <- data.frame(movies)
#https://stackoverflow.com/questions/27157137/dplyr-only-returning-one-row-when-using-summarize
movies.mean.rating <- movies %>% group_by(mpaa) %>% summarize(mean.rating = mean(rating))
movies.mean.rating 

```

Which year has the most total IMDB votes on the movies made that year?

```{r}
year.most.votes <- movies %>% dplyr::filter(votes == max(votes)) %>% select(year)
year.most.votes

#This does not work like SQL. Each action is executed individually then piped to the next function as input like in bash. Thus order does not matter. 
```

We are interested in finding which year created the most popular movies
relative to their budget. Create a function that takes a data.frame and
computes the average movie rating and divides it by the average budget.

```{r}
#var <- c(POP=with(df, sum(rating)/ sum(budget)))
pop.movies <- function(df){
  #Turn NA values into 0.
  df$budget[is.na(df$budget)] <- 0
  #Group on year then take mean rating for all movies for that year and divide by the mean of the budget for a particular year
  pop.df <- df %>% group_by(year) %>% summarize(popularity = mean(rating, na.rm=TRUE)/mean(budget, na.rm=TRUE))
  #Turn inf values into 0. Values that are essentially zero. 
  pop.df$popularity[is.infinite(pop.df$popularity)] <- 0
  return(pop.df)
}
years.pop <- pop.movies(movies)
years.pop <- years.pop[order(years.pop$popularity, decreasing=TRUE), ]
top.year.df <- head(years.pop, 1)
top.year <- top.year.df$year
top.year

```

Using your function defined above and the given data, what were the 6 years in which movies were made most efficiently between 1905 and 2005? 
(Hint: See the Baseball OBP example in Section 11.3.1.)

```{r}
years.pop <- pop.movies(movies)
years.pop <- years.pop[order(years.pop$popularity, decreasing=TRUE), ]
top.year.df <- head(years.pop, 6)
top.six.years <- top.year.df$year
top.six.years
```

Thought question: What concerns do you have with this validity of this
analysis?

```{r}
#I am not really sure if this a good indicator of how popular a movie is. Also, much of the data is missing. And another 
#Another movie database may have different ratings for movies. 
```